A microservices based approach for city traffic simulation

### 2019-11-03 papers/traffic simulation/paper.tex
A little more writings.

Figure \ref{fig:citysimrelations} depicts the city simulator in relation with the other entities. A notable exception is the web page. Its purpose is not to participate in the same information exchange the other have but to offer a visual interpretation of the way the city and the other actors are interacting with one another.

@@

The city actor represents a moving actor within a city. It can be a car which moves across the city, it can be a bike or it can be a pedestrian. Its naming suggests that it can be any entity or living being which moves within a city and interacts with the other entities or affects the other entities in some manner. A pedestrian would directly interact with other pedestrians but not with cars. A pedestrian would indirectly affect other cars by willing to walk over a crossing.

@@

An actor interacts, for the time being, with the city simulator by using a Go struct and a Go enum. They can be seen in listings \ref{lst:goactorstruct} and \ref{lst:goactorreports}.

\begin{lstlisting}[caption=Go struct for actor's report, label=lst:goactorreports]
const (   
    // ReportOnTheLine is the report sent by one agent to
    // notify the city that he is currently advancing
    // through one line.
    ReportOnTheLine = iota

@@

@@

>>>>

Figure \ref{fig:citysimrelations} depicts the city simulator in relation with the other entities. A notable exception is the web page. Its purpose is not to participate in the same information exchange the other entities have but to offer a visual interpretation of the way the city and the other actors are interacting with one another.

@@

The city actor represents a moving actor within a city. It can be a car which moves across the city, it can be a bike or it can be a pedestrian. Its naming suggests that it can be any entity or living being which moves within a city and interacts with the other entities or affects the other entities in some manner. A pedestrian would directly interact with other pedestrians but not with cars. A pedestrian would indirectly affect other cars by willing to walk over a street crossing.

@@

An actor interacts, for the time being, only with the city simulator by using a Go struct and a Go enum. They can be seen in listings \ref{lst:goactorstruct} and \ref{lst:goactorreports}. The message sent from one side to another has a general structure called \textit{Envelope}. It is meant to offer a top level message which can be serialized (or encoded, the way to do this in Golgang, if not gRPC, is the gob pacakge it offers out of the box) and passed around, enabling any party involved to understand what this message is about and how to decode it.

Listing \ref{lst:goenvelope} show the top level message. It contains a message type which instructs the reader what kind of message it has to deal with and the possible types are the second part of listing \ref{lst:goactorstruct}: \textit{SendReport}, \textit{AskForLine}, \textit{RespondWithLine}. Let's take them one by one. \textit{SendReport} represents a message sent from an actor to the city simulator and the \textit{Payload} contains the report seen in listing \ref{lst:goactorreports}.

\textit{AskForLine} is a message sent from an actor to the city simulator in which the actor asks about the density of any line. This way any actor can take conscious decisions on which route to go on when based on what lies ahead in terms of street densities. When a first route is known, between two desired points, the actor can ask about each line it has on that route. The city simulator will respond with the known density of it. If the actor desires, it can try to find another route by asking GraphHopper service to compute a new one but with an additional rule: avoid a certain point (street, junction, etc.). \textit{RespondWithLine} is the type of message which the city simulator sends back to an actor after it received an \textit{AskForLine} message.

\begin{lstlisting}[caption=Go enumerations for messaging, label=lst:goactorreports]
const (   
    // ReportOnTheLine is the report sent by one agent to
    // notify the city that he is currently advancing
    // through one line.
    ReportOnTheLine = iota

@@

\begin{lstlisting}[caption=Go top level struct (envelope), label=lst:goenvelope]
// Envelope is the container for different messages sent back
// and forth between an actor and a city
type Envelope struct {
    MessageType int
    Payload     interface{}
}
\end{lstlisting}

@@

The term orchestration means the handling of containers and microservices in order to bring coherence into their interaction. They have to run on multiple nodes (computers or virtual machines) and at the same time to communicate with one another. They need to be updated in place and without service disruption. Whenever one of them crash they have to restart as quickly as possible. They have to be able to discover themselves without dealing with intricancies of IP addresses, proxies, etc. They have to
